Social Participation Ontology: community documentation, enhancements and use examples

### 2015-01-11 paper.tex
feito geral, limpado, conferido
arrumado pequento typo de headers c ops

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figs/pubbyDer}
    %\includegraphics[width=\columnwidth]{figs/foo}
    \caption{Dereferencing an \ops\ class: the \uri\ is also an \urll, which, reached by \http, returns information for the user as shown. Also, if the client is not a browser, but a crawler or a linked data application, \pubby\ delivers plain \rdf, not user-friendly \html.}
    \label{fig:deref}
\end{figure}

@@

\section{Original diagram of \ops}\label{ap:dia}
Although deprecated, Figure~\ref{fig:diaorig} is the basis of \vcps\ and \ops. It is displayed here for completeness of exposition and as support for discussions within this article. 
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/diagramaOriginal}
    \caption{Original \vcps diagram. Although there were substantial \owl\ modifications, the main difference in the diagram is that the class \texttt{Role} was removed, as a \texttt{Role} is not able to start, execute or support anything. That is done by the Social Actor, as exposed in Figure~\ref{fig:v1}.}
    \label{fig:diaorig}
\end{figure*}

\section{Script for constructing current \ops}\label{ap:script}
Preliminary \ops\ was done with \protege\ software~\cite{protege}. Current \ops\ is the output of a Python script~\cite{opsScript}. Actually, this article, latex files, the \owl\ code, the \python script and auxiliary files are in a public git repository~\cite{opsRepo}, as is the common practice of the first author of this article.

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figs/pubbyDer}
    \caption{Dereferencing an \ops\ class: the \uri\ is also an \urll, which, reached by \http, returns information for the user as shown. Also, if the client is not a browser, but a crawler or a linked data application, \pubby\ delivers plain \rdf, not user-friendly \html.}
    \label{fig:deref}
\end{figure}

@@

\section{Original diagram of OPS}\label{ap:dia}
Although deprecated, Figure~\ref{fig:diaorig} is the basis of \vcps\ and \ops. It is displayed here for completeness of exposition and as support for discussions within this article. 
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/diagramaOriginal}
    \caption{Original \vcps diagram. Although there were substantial \owl\ modifications, the main difference in the diagram is that the class \texttt{Role} was removed, as a \texttt{Role} is not able to start, execute or support anything. That is done by the Social Actor, as exposed in Figure~\ref{fig:v1}.}
    \label{fig:diaorig}
\end{figure*}

\section{Script for constructing current OPS}\label{ap:script}
Preliminary \ops\ was done with \protege\ software~\cite{protege}. Current \ops\ is the output of a Python script~\cite{opsScript}. Actually, this article, latex files, the \owl\ code, the \python script and auxiliary files are in a public git repository~\cite{opsRepo}, as is the common practice of the first author of this article.
